%The proposal should list the names of all group members, provide a working title for your project and describe what it seeks to do. You do not need to include specific implementation details, but you should fully describe your project goals so that a reader would understand what you are trying to create. It should also include a timeline for completing your project by the due date. Explain your design choices. Your proposal must be turned in as a hard copy and should not exceed two pages. You should also include ER diagram that provides a more appropriate way of explaining your ideas.



\documentclass[12pt]{article}
\title{CSC490 Design Project Proposal}
\author{Lily Friedberg \\ Oscar Suen}
\date{\today}
\begin{document}
\maketitle

\section{Working Title}
Econometrics 4 Kids
\section{Description}
The World Bank has an enormous quantity of data about the global economy, but it is woefully inaccessible to the common man. In this project, our goal will be to help visualise this and analogous data graphically both synchronically and diachronically. Our final product should include pages to view data in one year, as well as about the current state of each country, and dynamically generate and display graphs with user-selected metrics on the x- and y- axes. Additionally, users will be able to define their own metrics in terms of extant ones (eg, the misery index), and graph these. In order to do this, we will define a syntax and design a UI which will make this as intelligible and accessible as possible.
\section{Timeline}
By Nov. 8, we should have the database built and populated. \\
By Nov. 11, all necessary pages and files should exist. \\
By Nov. 13, the python should talk to the database, the country pages should be finished. \\
By Nov. 16, the project should be functional, with only aesthetic work and bug fixes left. \\
The Project is due Nov. 17.
\section{ER Diagram}

\end{document}